\tool

### 2018-04-22 paper/paper.tex
Minor intro updates

Although software quality is important, software engineering tools created to improve code quality are often ignored by developers~\cite{Ivanov2017Gaps}. Previous work explores barriers preventing software engineers from utilizing useful tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more to help complete programming tasks. Additionally, Tilley and colleagues presented challenges for professional software developers in industry adopting software engineering tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}. One barrier to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of tool awareness in the software engineering industry can lead to the production of poor-quality applications, inconvenienced users, and significant amounts of time and money spent fixing errors. Many existing automated approaches have been implemented to increase awareness of software tools and features, but Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{MurphyHill2011PeerInteraction}.

To help solve the tool discovery problem among software engineers, we developed an approach for making automated tool recommendations. Our approach integrates characteristics of peer interactions and software engineering practices to suggest useful tools to developers. We base our technique on three main design pillars- \textit{commend}, \textit{apprehend}, and \textit{recommend}. These principles differentiate our approach from existing techniques because they can be applied to many different types of software engineering tools and integrate user receptiveness to make customized recommendations to developers.

@@

To evaluate our approach, we implemented \tool. The initial implementation of \tool~for this study recommends \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code, to developers on GitHub\footnote{https://github.com}, a popular code hosting and collaboration website. We measured the effectiveness of our system by observing the frequency of recommendations and how developers reacted to receiving suggestions for tools from our system. This research makes the following contributions:

>>>>

Although software quality is important, software engineering tools created to improve code quality are often ignored by developers~\cite{Ivanov2017Gaps}. Tilley and colleagues suggest tool adoption should be one of the most important goals of software engineering research, and present challenges preventing professional developers from adopting programming tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}. Furthermore, researchers have explored barriers preventing software engineers from utilizing useful tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more. One barrier to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of tool awareness in the software engineering industry can lead to poor-quality applications, inconvenienced users, and wasted time and money fixing errors. Automated approaches have been developed to increase awareness of software tools and features, however Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{MurphyHill2011PeerInteraction}.

To help solve the tool discovery problem among software engineers, we developed an approach for making automated tool recommendations. Our approach integrates characteristics of peer interactions and software engineering practices to suggest useful tools to developers. We base our technique on three design pillars: \textit{commend}, \textit{apprehend}, and \textit{recommend}. These principles allow our approach to be applied to a variety software engineering tools and to make customized recommendations to developers. Our goal is for researchers and toolsmiths to implement this approach to increase awareness and adoption of their tools.

@@

To evaluate our approach, we implemented \tool. The initial implementation of \tool~for this study recommends \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code, to developers on GitHub\footnote{https://github.com}, a popular code hosting and collaboration website. We measure the effectiveness of our approach by observing the frequency of recommendations and how developers react to receiving suggestions for tools from our system compared to other recommendation methods. This research makes the following contributions:
